Estimating Access to Rabies Post-Exposure Prophylaxis in Madagascar

### 2019-03-20 accessPEP.Rmd
with section S7 on vials and bite incidence per catchment

@@

c / d

@@

```{r fig M4 burden, cache = TRUE}
## District travel times
dist_ttimes <- read.csv("output/district_temp_scenario_20190212_181056.csv", row.names = 1)
comm_ttimes <- read.csv("output/commune_temp_scenario_20190212_182810.csv", row.names = 1)

@@

## Group commune results to district level
colnames(results_comm_med) <- gsub("results.", "", colnames(results_comm_med))
results_comm_med %>%
  left_join(select(comm_data, mdg_dis_co, mdg_cm_), 
            by = c("names" = "mdg_cm_")) %>%
  group_by(scenario, mdg_dis_co) %>%
  summarize(deaths_mean = sum(deaths_mean, na.rm = TRUE), 
            deaths_upperCI = sum(deaths_upperCI, na.rm = TRUE),
            deaths_lowerCI = sum(deaths_lowerCI, na.rm = TRUE),
            averted_mean = sum(averted_mean, na.rm = TRUE), 
            averted_upperCI = sum(averted_upperCI, na.rm = TRUE),
            averted_lowerCI = sum(averted_lowerCI, na.rm = TRUE)) %>%
  rename(names = mdg_dis_co) -> results_comm_summarized
results_comm_summarized$model <- "Commune"
colnames(results_dist_med) <- gsub("results.", "", colnames(results_dist_med))
results_dist_med %>%
  mutate(model = "District") %>%
  select(scenario, names, deaths_mean, deaths_lowerCI, deaths_upperCI, 
         averted_mean, averted_lowerCI, averted_upperCI,
         model) -> results_dist_med
results_all <- bind_rows(results_dist_med, results_comm_summarized)
results_all %>%
  left_join(select(mada_district@data, district, mdg_dis_co, ttimes_weighted),
            by = c("names" = "mdg_dis_co")) -> results_all

## Plot national level burden
results_all %>% 
  group_by(scenario, model) %>% 
  summarize(deaths_mean = sum(deaths_mean, na.rm = TRUE), 
            deaths_upperCI = sum(deaths_upperCI, na.rm = TRUE),
            deaths_lowerCI = sum(deaths_lowerCI, na.rm = TRUE), 
            averted_mean = sum(averted_mean, na.rm = TRUE), 
            averted_upperCI = sum(averted_upperCI, na.rm = TRUE),
            averted_lowerCI = sum(averted_lowerCI, na.rm = TRUE)) -> results_natl

## Baseline results
results_all %>% filter(scenario == 0) -> results_all_base
results_all_base %>%
  left_join(dist_data, by = c("names" = "district")) -> results_all_base
ggplot(filter(results_all_base, !is.na(district)), 
       aes(y = deaths_mean/pop*1e5, x = reorder(district, ttimes_weighted), 
                              color = model)) +
  geom_pointrange(aes(ymin = deaths_lowerCI, ymax = deaths_upperCI), fatten = 2) +
  xlab("Districts ordered by travel times \n (low to high)") +
  ylab("Annual deaths per 100k persons") +
  coord_flip() +
  scale_color_manual(values = c("district" = alpha("purple", 0.5), 
                                "commune" = alpha("navy", 0.5)), 
                     name = "Scale") +
  theme(axis.text.y = element_blank()) +
  labs(tag = "A") -> d

@@

burden <- d / p

burden

ggsave("figs/burden_maps.jpeg", burden, device = "jpeg", width = 10, height = 10)

@@

We find that expanding access to PEP reduces burden of rabies death, but this effect decays as ARMC are added, saturating after about approximately 200 clinics (or 2 ARMC per district). This effect is more pronouned for the commune level model than for the district model. These patterns are also generally robust to our assumptions, although the decrease in deaths saturates quickly for the district model as $p_rabid$ and $rho_max$ decrease?

@@

## local cluster
library(doParallel)
# Calculate the number of cores
no_cores <- detectCores() - 1
# Initiate cluster
cl <- makeCluster(no_cores)
registerDoParallel(cl)
system.time({comm <- sim.throughput(bites = comm_master$bites_comm, nsims = 3)})
system.time({dist <- sim.throughput(bites = comm_master$bites_dist, nsims = 3)})
comm$model <- "commune"
dist$model <- "district"

@@

```{r fig M5 scenario deaths and vials, cache = TRUE}
## Plotting national level
ggplot(data = results_natl, aes (x = scenario, y = deaths_mean, color = model)) +
  geom_line() +
  geom_ribbon(aes(ymin = deaths_upperCI, ymax = deaths_lowerCI, 
                  color = NULL, fill = model),
              alpha = 0.5) +
  scale_color_manual(values = c("district" = "blue", 
                                "commune" = "purple"), 
                     guide = "none") +
  scale_fill_manual(values = c("district" = "blue", 
                                "commune" = "purple")) +
  guides(color = guide_legend(), 
         fill = guide_legend(override.aes = list(linetype = 1))) +
  xlab("# of Additional ARMC") +
  ylab("Annual deaths \n due to rabies nationally") +
  labs(tag = "A") -> e

ggplot(data = throughput_scenario, aes (x = scenario, y = mean_vials, color = model)) +
  geom_line() +
  geom_ribbon(aes(ymin = lower_vials, ymax = upper_vials, 
                  color = NULL, fill = model),
              alpha = 0.5) +
  scale_color_manual(values = c("district" = "blue", 
                                "commune" = "purple"), 
                     guide = "none") +
  scale_fill_manual(values = c("district" = "blue", 
                                "commune" = "purple")) +
  guides(color = guide_legend(), 
         fill = guide_legend(override.aes = list(linetype = 1))) +
  xlab("# of Additional ARMC") +
  ylab("Mean estimate of vials needed") +
  labs(tag = "B")

@@

ggplot(data = results_natl_all, aes (x = scenario, y = mean_vials/averted_mean, color = model)) +
  geom_line() +
  geom_ribbon(aes(ymin = lower_vials/averted_mean, ymax = upper_vials/averted_mean, 
                  color = NULL, fill = model),
              alpha = 0.5) +
  scale_color_manual(values = c("district" = "blue", 
                                "commune" = "purple"), 
                     guide = "none") +
  scale_fill_manual(values = c("district" = "blue", 
                                "commune" = "purple")) +
  guides(color = guide_legend(), 
         fill = guide_legend(override.aes = list(linetype = 1))) +
  xlab("# of Additional ARMC") +
  ylab("Estimate of vials \n per death averted") +
  labs(tag = "B") -> f

e / f

comm_mat %>%
  left_join(comm_ttimes) %>%
  left_join(select(mada_communes@data, pop = MDG__201, mdg_cm_)) %>%
  mutate(exp_bites = inv.logit(B_ttimes_mada*ttimes/60 + B_0_mada)*pop) %>%
  group_by(scenario, catchment) %>%
  summarize(pop = sum(pop, na.rm = TRUE), ttimes = mean(ttimes, na.rm = TRUE), 
            bites = sum(exp_bites, na.rm = TRUE), n_comms = n()) %>%
  mutate(model = "commune") %>%
  drop_na(catchment) -> comm_cmod
pop_natl <- sum(mada_district$pop2015adj)
comm_mat %>%
  left_join(comm_ttimes) %>%
  left_join(select(mada_communes@data, pop = MDG__201, mdg_cm_)) %>%
  mutate(exp_bites = inv.logit(B_ttimes_dist*ttimes/60 + B_0_dist)*pop) %>%
  group_by(scenario, catchment) %>%
  summarize(pop = sum(pop, na.rm = TRUE), ttimes = mean(ttimes, na.rm = TRUE), 
            bites = sum(exp_bites, na.rm = TRUE), n_comms = n()) %>%
  mutate(model = "district") %>%
  drop_na(catchment) -> comm_dmod
bites_exp <- bind_rows(comm_cmod, comm_dmod)
bites_exp %>%
  group_by(scenario, model) %>%
  summarize(bites = sum(bites)/pop_natl*1e5) %>%
  ggplot(., aes(x = scenario, y = bites, color = model)) +
  geom_line() +
  ylab("Reported bites \n per 100k persons") +
  xlab("# Additional ARMC")

comm_mat %>%
  left_join(comm_ttimes) %>%
  left_join(select(mada_communes@data, pop = MDG__201, mdg_cm_)) %>%
  mutate(exp_bites = inv.logit(B_ttimes_mada*ttimes/60 + B_0_mada)*pop) -> comm_exp

## Do district one
## Get catchment
catch_scenario <- read.csv("output/temp_ARMC.csv", row.names = 1)
dist_ttimes <- read.csv("output/district_temp_scenario_20190212_181056.csv", row.names = 1)
dist_ttimes <- cbind(dist_ttimes[, 1], dist_ttimes)
names(dist_ttimes)[1] <- "result.0"
dist_mat <- matrix(NA, nrow(dist_ttimes), ncol(dist_ttimes))
dist_mat[, 1] <- as.character(mada_district$CTAR)

for (i in 2:ncol(dist_ttimes)){
  dist_mat[, i] <- ifelse(dist_ttimes[, i] < dist_ttimes[, i - 1], as.character(catch_scenario$CTAR[i - 1]), 
                          dist_mat[, 1])
}

dist_mat <- as.data.table(dist_mat)
dist_mat$mdg_dis_co <- mada_district$mdg_dis_co
dist_mat <- melt(dist_mat, id.vars = "mdg_dis_co", value.name = "catchment", variable.name = "scenario")
dist_mat$scenario <- as.numeric(gsub("V", "", dist_mat$scenario)) - 1
dist_ttimes <- as.data.table(dist_ttimes)
dist_ttimes$mdg_dis_co <- mada_district$mdg_dis_co
dist_ttimes <- melt(dist_ttimes, id.vars = "mdg_dis_co", value.name = "ttimes", variable.name = "scenario")
dist_ttimes$scenario <- as.numeric(gsub("result.", "", dist_ttimes$scenario))
# 
# dist_mat %>%
#   left_join(dist_ttimes) %>%
#   left_join(select(mada_district@data, pop = pop2015adj, mdg_dis_co)) %>%
#   mutate(exp_bites = inv.logit(B_ttimes_dist*ttimes/60 + B_0_dist)*pop) %>%
#   group_by(scenario, catchment) %>%
#   summarize(bites = sum(exp_bites, na.rm = TRUE)) %>%
#   drop_na(catchment) -> dist_master

dist_mat %>%
  left_join(dist_ttimes) %>%
  left_join(select(mada_district@data, pop = pop2015adj, mdg_dis_co)) %>%
  mutate(exp_bites = inv.logit(B_ttimes_dist*ttimes/60 + B_0_dist)*pop) -> dist_exp
ggplot(data = filter(dist_exp, scenario %in% c(0, 1, 10, 50, 100, 200)), 
       aes(x = ttimes/60, y = as.factor(scenario))) +
  ggridges::geom_density_ridges()
dist_exp$scale <- "District"
comm_exp$scale <- "Commune"

check_exps <- bind_rows(select(comm_exp, scenario, ttimes, pop, scale, exp_bites), 
                        select(dist_exp, scenario, ttimes, pop, scale, exp_bites))
ggplot(data = filter(check_exps, scenario %in% c(0, 1, 10, 50, 100, 200)), 
       aes(x = ttimes/60, y = as.factor(scenario), fill = scale)) +
  ggridges::geom_density_ridges(alpha = 0.5)

ggplot(data = filter(check_exps, scenario %in% c(0, 1, 10, 50, 100, 200)), 
       aes(x = exp_bites/pop*1e5, y = as.factor(scenario), fill = scale)) +
  ggridges::geom_density_ridges(alpha = 0.5)

@@

### S1. Estimates of reporting
```{r}
## Getting other data
rep_data <- get.reporting(ctar_data, ctar_metadata, start_date = ymd("2014-01-01"), 
                          end_date = ymd("2017-12-31"), 
                          threshold = 15)
clinic_reporting <- rep_data[["clinic_reporting"]]
patient_ts <- rep_data[["patient_ts"]]
date_mat <- rep_data[["date_mat"]]
dose_mat <- rep_data[["dose_mat"]]
doses_wide <- rep_data[["doses_wide"]]

@@

p + n

@@

```{r excluding contacts}
ctar_contacts <- get.contacts(ctar_data, times_sd = 3)
patient_ts <- ctar_contacts[["patient_ts"]]
patient_ts <- patient_ts[patient_ts$ctar != "Tsiroanomandidy", ]
A <- ggplot(data = drop_na(patient_ts, exclude), aes(x = ctar, y = n, color = as.factor(exclude))) +
  scale_color_manual(name = "Exclude", values = c("navy", "red"), labels = c("No", "Yes")) +
  ylab("Number of patients per day") +
  xlab("ARMC") +
  geom_jitter(alpha = 0.5, width = 0.25) +
  coord_flip() +
  labs(tag = "A")

@@

A + B

@@

```{r models, cache = TRUE}
## Exclude for comm data!
comm_covars <- filter(comm_data, exclude == 0)

@@

ggplot(filter(preds_data, pop_predict != "onlyPop"), aes(x = observed, y = predicted, color = scale)) + 
  geom_point(alpha = 0.5) +
  geom_abline(slope = 1, intercept = 0, linetype = 2, color = "grey") +
  scale_color_manual(values = c("blue", "purple", "red"), name = "Scale") +
  facet_grid(pop_predict ~ covar_name, scales = "free_x", 
             labeller = labeller(pop_predict = as_labeller(mod_names), 
                                 covar_name = as_labeller(covar_names)), drop = TRUE) +
  expand_limits(y = 0) +
  xlab("Observed bites") +
  ylab("Predicted bites")

ggplot(filter(preds_data, pop_predict == "onlyPop"), aes(x = observed, y = predicted, color = scale)) + 
  geom_point(alpha = 0.5) +
  geom_abline(slope = 1, intercept = 0, linetype = 2, color = "grey") +
  scale_color_manual(values = c("blue", "purple", "red"), name = "Scale") +
  facet_grid(pop_predict ~ covar_name, scales = "free_x", 
             labeller = labeller(pop_predict = as_labeller(mod_names), 
                                 covar_name = as_labeller(covar_names)), drop = TRUE) +
  expand_limits(y = 0) +
  xlab("Observed bites") +
  ylab("Predicted bites")

@@

```{r rles and cut-offs, cache = TRUE}
consec_days <- c(5, 15, 30, 60)
contact_cutoff <- c(1, 3, 10, 100)

@@

ggplot(preds_fixed_df, aes(x = covar, y = predicted, group = interaction(consec_days, scale, contact_cutoff), 
                           color = consec_days, linetype = scale), alpha = 0.2) + 
  geom_line() + 
  scale_color_gradient(low = "pink", high = "red", name = "Reporting cut-off") +
  scale_linetype(name = "Model") +
  xlab("Travel time (hrs)") +
  ylab("Reported bites per \n 100,000 persons") +
  facet_grid( ~ contact_cutoff)

ggplot(preds_data_df, aes(x = observed, y = predicted,
                       color = scale)) + 
  geom_point(alpha = 0.5) +
  geom_abline(slope = 1, intercept = 0, linetype = 2, color = "grey") +
  scale_color_manual(values = c("blue", "purple", "red"), name = "Scale") +
  facet_grid(contact_cutoff ~ consec_days, scales = "free") +
  xlab("Observed bites") +
  ylab("Predicted bites")

@@

### S5. Sensitity analyses for burden estimates
#### District
```{r scaling w/ pop, cache = TRUE}
## Dist ttimes
dist_ttimes <- read.csv("output/district_temp_scenario_20190212_181056.csv", row.names = 1)
dist_ttimes <- as.data.table(dist_ttimes)
dist_ttimes$mdg_dis_co <- as.character(mada_district$mdg_dis_co)
dist_ttimes <- melt(dist_ttimes, id.vars = "mdg_dis_co", value.name = "ttimes", variable.name = "scenario")
dist_ttimes$scenario <- as.numeric(gsub("result.", "", dist_ttimes$scenario))
dist_ttimes <- rbind(dist_ttimes, 
                       as.data.frame(list(mdg_dis_co = dist_catchments$mdg_dis_co, scenario = 0,
                                          ttimes = dist_catchments$ttimes_weighted)))
dist_ttimes %>%
  left_join(select(mada_district@data, mdg_dis_co, district, pop = pop2015adj)) -> dist_ttimes

@@

#### Commune

@@

```{r scaling factor}
A_dist / A_comm
```

```{r differences with ttimes}
C_dist / C_comm
```

```{r national burden baseline}
B_dist / B_comm

@@

```{r national burden scenario}
D_dist / D_comm

@@

#### Difference between scale examples

```{r scale example}
## Comparing scales
p_rabid_vals <- seq(0.2, 0.6, by = 0.05)
hdr_vals <- seq(5, 25, by = 5)

@@

ggplot(reporting, aes(x = reorder(names, ttimes), y = reporting, color = params)) +
  geom_boxplot(outlier.shape = NA) +
  scale_color_manual(values = c(alpha("blue", 0.5), alpha("purple", 0.5)), name = "Parameters") +
  xlab("Districts ordered by travel times \n (low to high)") +
  ylab("Reporting of rabid exposures") +
  facet_wrap(~ scale) +
  coord_flip() +
  theme(axis.text.y = element_blank())

@@

>>>>

We compare the estimates of reporting generated from the commune model vs. the district model by summing the commune level reporting estimates weighted by the proportion of the district population they are applied to such that:

\begin{equation}
           \rho_d = \sum \limits_{j=1}\frac{rho_j*P_j}{P_d}
\begin{equation}

@@

figM3 <- c / d 
figM3 
ggsave("figs/M3.jpeg", figM3, device = "jpeg", width = 7, height = 7)

@@

```{r run burden and scenario, cache = TRUE}
## District travel times
dist_ttimes <- read.csv("output/district_temp_scenario_20190212_181056.csv", row.names = 1)
comm_ttimes <- read.csv("output/commune_temp_scenario_20190212_182810.csv", row.names = 1)

@@

## Group commune results to district level
colnames(results_comm_med) <- gsub("results.", "", colnames(results_comm_med))
results_comm_med %>%
  left_join(select(comm_data, mdg_dis_co, mdg_cm_), 
            by = c("names" = "mdg_cm_")) %>%
  group_by(scenario, mdg_dis_co) %>%
  summarize(deaths_mean = sum(deaths_mean, na.rm = TRUE), 
            deaths_upperCI = sum(deaths_upperCI, na.rm = TRUE),
            deaths_lowerCI = sum(deaths_lowerCI, na.rm = TRUE),
            averted_mean = sum(averted_mean, na.rm = TRUE), 
            averted_upperCI = sum(averted_upperCI, na.rm = TRUE),
            averted_lowerCI = sum(averted_lowerCI, na.rm = TRUE)) %>%
  rename(names = mdg_dis_co) -> results_comm_summarized
results_comm_summarized$model <- "Commune"
colnames(results_dist_med) <- gsub("results.", "", colnames(results_dist_med))
results_dist_med %>%
  mutate(model = "District") %>%
  select(scenario, names, deaths_mean, deaths_lowerCI, deaths_upperCI, 
         averted_mean, averted_lowerCI, averted_upperCI,
         model) -> results_dist_med
results_all <- bind_rows(results_dist_med, results_comm_summarized)
results_all %>%
  left_join(select(mada_district@data, district, mdg_dis_co, ttimes_weighted),
            by = c("names" = "mdg_dis_co")) -> results_all 
```

``` {r fig M4 baseline burden, cache = TRUE}
## Plot national level burden
results_all %>% 
  group_by(scenario, model) %>% 
  summarize(deaths_mean = sum(deaths_mean, na.rm = TRUE), 
            deaths_upperCI = sum(deaths_upperCI, na.rm = TRUE),
            deaths_lowerCI = sum(deaths_lowerCI, na.rm = TRUE), 
            averted_mean = sum(averted_mean, na.rm = TRUE), 
            averted_upperCI = sum(averted_upperCI, na.rm = TRUE),
            averted_lowerCI = sum(averted_lowerCI, na.rm = TRUE)) -> results_natl

## Baseline results
results_all %>% filter(scenario == 0) -> results_all_base
results_all_base %>%
  left_join(dist_data, by = c("names" = "district")) %>%
  drop_na(names) -> results_all_base
ggplot(results_all_base, 
       aes(y = deaths_mean/pop*1e5, x = reorder(district, ttimes_weighted), 
                              color = model)) +
  geom_pointrange(aes(ymin = deaths_lowerCI/pop*1e5, ymax = deaths_upperCI/pop*1e5), fatten = 2) +
  xlab("Districts ordered by travel times \n (low to high)") +
  ylab("Annual deaths per 100k persons") +
  coord_flip() +
  scale_color_manual(values = c(alpha("navy", 0.5), alpha("purple", 0.5)), 
                     name = "Scale") +
  theme(axis.text.y = element_blank()) +
  labs(tag = "A") -> d

@@

figM4 <- d / p

figM4

ggsave("figs/M4.jpeg", figM4, device = "jpeg", width = 10, height = 10)

@@

We find that expanding access to PEP reduces burden of rabies death, but this effect decays as ARMC are added, saturating after about approximately 200 clinics (or 2 ARMC per district). This effect is more pronouned for the commune level model than for the district model. These patterns are also generally robust to our assumptions, although the decrease in deaths saturates quickly for the district model as $p_rabid$ and $rho_max$ decrease? Vials...

@@

## local cluster
library(doParallel)
# Calculate the number of cores
no_cores <- detectCores() - 1
# Initiate cluster
cl <- makeCluster(no_cores)
registerDoParallel(cl)
system.time({comm <- sim.throughput(bites = comm_master$bites_comm, nsims = 3)})
system.time({dist <- sim.throughput(bites = comm_master$bites_dist, nsims = 3)})
comm$model <- "Commune"
dist$model <- "District"

@@

```{r fig M5 scenario deaths and vials, cache = TRUE}
## Plotting national level
ggplot(data = results_natl, aes (x = scenario, y = deaths_mean, color = model)) +
  geom_line() +
  geom_ribbon(aes(ymin = deaths_upperCI, ymax = deaths_lowerCI, 
                  color = NULL, fill = model),
              alpha = 0.5) +
  scale_color_manual(values = c("navy", "purple"), 
                     guide = "none") +
  scale_fill_manual(values = c("navy", "purple")) +
  guides(color = guide_legend(), 
         fill = guide_legend(override.aes = list(linetype = 1))) +
  xlab("# of Additional ARMC") +
  ylab("Annual deaths \n due to rabies nationally") +
  labs(tag = "A") -> e

@@

ggplot(data = results_natl_all, aes (x = scenario, y = mean_vials/averted_mean, color = model)) +
  geom_line() +
  geom_ribbon(aes(ymin = lower_vials/averted_mean, ymax = upper_vials/averted_mean, 
                  color = NULL, fill = model),
              alpha = 0.5) +
  scale_color_manual(values = c("navy", "purple"), 
                     guide = "none") +
  scale_fill_manual(values = c("navy", "purple")) +
  guides(color = guide_legend(), 
         fill = guide_legend(override.aes = list(linetype = 1))) +
  xlab("# of Additional ARMC") +
  ylab("Estimate of vials \n per death averted") +
  labs(tag = "B") -> f

figM5 <- e / f
ggsave("figs/M5.jpeg", figM5, device = "jpeg")

@@

### S1. Estimates of reporting
```{r fig S1.1 reporting cut-offs}
## Getting other data
rep_data <- get.reporting(ctar_data, ctar_metadata, start_date = ymd("2014-01-01"), 
                          end_date = ymd("2017-12-31"), 
                          threshold = 15)
clinic_reporting <- rep_data[["clinic_reporting"]]
patient_ts <- rep_data[["patient_ts"]]
date_mat <- rep_data[["date_mat"]]
dose_mat <- rep_data[["dose_mat"]]
doses_wide <- rep_data[["doses_wide"]]

@@

figS1.1 <- p + n
figS1.1
ggsave("figs/figS1.1.jpeg", figS1.1, device = "jpeg")

@@

```{r fig S2.1 excluding contacts}
ctar_contacts <- get.contacts(ctar_data, times_sd = 3)
patient_ts <- ctar_contacts[["patient_ts"]]
patient_ts <- patient_ts[patient_ts$ctar != "Tsiroanomandidy", ]
A <- ggplot(data = drop_na(patient_ts, exclude), aes(x = ctar, y = n, color = as.factor(exclude))) +
  scale_color_manual(name = "Exclude", values = c("navy", "red"), labels = c("No", "Yes")) +
  ylab("Number of patients per day") +
  xlab("ARMC") +
  geom_jitter(alpha = 0.5, width = 0.25) +
  coord_flip() +
  labs(tag = "A")

@@

figS2.1 <- A + B
ggsave("figs/S2.1.jpeg", figS2.1, device = "jpeg")
```

@@

```{r figs S3.1 and S3. 2comparing models, cache = TRUE}
## Exclude for comm data!
comm_covars <- filter(comm_data, exclude == 0)

@@

A <- ggplot(filter(preds_data, pop_predict != "onlyPop"), aes(x = observed, y = predicted, color = scale)) + 
  geom_point(alpha = 0.5) +
  geom_abline(slope = 1, intercept = 0, linetype = 2, color = "grey") +
  scale_color_manual(values = c("blue", "purple", "red"), name = "Scale") +
  facet_grid(pop_predict ~ covar_name, scales = "free_x", 
             labeller = labeller(pop_predict = as_labeller(mod_names), 
                                 covar_name = as_labeller(covar_names)), drop = TRUE) +
  expand_limits(y = 0) +
  xlab("Observed bites") +
  ylab("Predicted bites")

B <- ggplot(filter(preds_data, pop_predict == "onlyPop"), aes(x = observed, y = predicted, color = scale)) + 
  geom_point(alpha = 0.5) +
  geom_abline(slope = 1, intercept = 0, linetype = 2, color = "grey") +
  scale_color_manual(values = c("blue", "purple", "red"), name = "Scale") +
  facet_grid(pop_predict ~ covar_name, scales = "free_x", 
             labeller = labeller(pop_predict = as_labeller(mod_names), 
                                 covar_name = as_labeller(covar_names)), drop = TRUE) +
  expand_limits(y = 0) +
  xlab("Observed bites") +
  ylab("Predicted bites")

A
B
ggsave("figs/figS3.1.jpeg", A, device = "jpeg")
ggsave("figs/figS3.2.jpeg", B, device = "jpeg")

@@

```{r fig S4.1 and S4.2 rles and cut-offs, cache = TRUE}
consec_days <- c(5, 15, 30, 60)
contact_cutoff <- c(1, 3, 10, 100)

@@

A <- ggplot(preds_fixed_df, aes(x = covar, y = predicted, group = interaction(consec_days, scale, contact_cutoff), 
                           color = consec_days, linetype = scale), alpha = 0.2) + 
  geom_line() + 
  scale_color_gradient(low = "pink", high = "red", name = "Reporting cut-off") +
  scale_linetype(name = "Model") +
  xlab("Travel time (hrs)") +
  ylab("Reported bites per \n 100,000 persons") +
  facet_grid( ~ contact_cutoff)

B <- ggplot(preds_data_df, aes(x = observed, y = predicted,
                       color = scale)) + 
  geom_point(alpha = 0.5) +
  geom_abline(slope = 1, intercept = 0, linetype = 2, color = "grey") +
  scale_color_manual(values = c("blue", "purple", "red"), name = "Scale") +
  facet_grid(contact_cutoff ~ consec_days, scales = "free") +
  xlab("Observed bites") +
  ylab("Predicted bites")
A
B
ggsave("figs/figS4.1.jpeg", A, device = "jpeg")
ggsave("figs/figS4.2.jpeg", B, device = "jpeg")

@@

### S5. Sensitity analyses for burden estimates
```{r district scaling w/ pop, cache = TRUE}
## Dist ttimes
dist_ttimes <- read.csv("output/district_temp_scenario_20190212_181056.csv", row.names = 1)
dist_ttimes <- as.data.table(dist_ttimes)
dist_ttimes$mdg_dis_co <- as.character(mada_district$mdg_dis_co)
dist_ttimes <- melt(dist_ttimes, id.vars = "mdg_dis_co", value.name = "ttimes", variable.name = "scenario")
dist_ttimes$scenario <- as.numeric(gsub("result.", "", dist_ttimes$scenario))
dist_ttimes <- rbind(dist_ttimes, 
                       as.data.frame(list(mdg_dis_co = dist_catchments$mdg_dis_co, scenario = 0,
                                          ttimes = dist_catchments$ttimes_weighted)))
dist_ttimes %>%
  left_join(select(mada_district@data, mdg_dis_co, district, pop = pop2015adj)) -> dist_ttimes

@@

@@

```{r fig S5.1 scaling factor}
figS5.1 <- A_dist / A_comm
figS5.1
ggsave("figs/figS5.1.jpeg", figS5.1, device = "jpeg")

@@

```{r fig S5.2 differences with ttimes}
figS5.2 <- C_dist / C_comm
figS5.2
ggsave("figs/figS5.2.jpeg", figS5.2, device = "jpeg")

@@

```{r fig S5.3 national burden baseline}
figS5.3 <-B_dist / B_comm
figS5.3
ggsave("figs/figS5.3.jpeg", figS5.3, device = "jpeg")
```

```{r fig S5.4 national burden scenario}
figS5.4 <- D_dist / D_comm
figS5.4
ggsave("figs/figS5.4.jpeg", figS5.4, device = "jpeg")
```

### S6: Difference between reporting estimates for each model

```{r fig S6.1 scale example}
## Comparing scales
p_rabid_vals <- seq(0.2, 0.6, by = 0.05)
hdr_vals <- seq(5, 25, by = 5)

@@

figS6.1 <- ggplot(reporting, aes(x = reorder(names, ttimes), y = reporting, color = params)) +
  geom_boxplot(outlier.shape = NA) +
  scale_color_manual(values = c(alpha("blue", 0.5), alpha("purple", 0.5)), name = "Parameters") +
  xlab("Districts ordered by travel times \n (low to high)") +
  ylab("Reporting of rabid exposures") +
  facet_wrap(~ scale) +
  coord_flip() +
  theme(axis.text.y = element_blank())

figS6.1
ggsave("figs/figS6.1.jpeg", figS6.1, device = "jpeg")

@@

### S7: Vial estimates and total reported bites with PEP expansion
```{r fig S7.1 bites and vials}
comm_mat %>%
  left_join(comm_ttimes) %>%
  left_join(select(mada_communes@data, pop = MDG__201, mdg_cm_)) %>%
  mutate(exp_bites = inv.logit(B_ttimes_mada*ttimes/60 + B_0_mada)*pop) %>%
  group_by(scenario, catchment) %>%
  summarize(pop = sum(pop, na.rm = TRUE), ttimes = mean(ttimes, na.rm = TRUE),
            bites = sum(exp_bites, na.rm = TRUE), n_comms = n()) %>%
  mutate(model = "Commune") %>%
  drop_na(catchment) -> comm_cmod
comm_mat %>%
  left_join(comm_ttimes) %>%
  left_join(select(mada_communes@data, pop = MDG__201, mdg_cm_)) %>%
  mutate(exp_bites = inv.logit(B_ttimes_dist*ttimes/60 + B_0_dist)*pop) %>%
  group_by(scenario, catchment) %>%
  summarize(pop = sum(pop, na.rm = TRUE), ttimes = mean(ttimes, na.rm = TRUE),
            bites = sum(exp_bites, na.rm = TRUE), n_comms = n()) %>%
  mutate(model = "District") %>%
  drop_na(catchment) -> comm_dmod
bites_exp <- bind_rows(comm_cmod, comm_dmod)
pop_natl <- sum(mada_district$pop2015adj)

ggplot(data = filter(bites_exp, scenario %in% c(0, 1, 10, 50, 100, 200)),
       aes(x = bites/pop*1e5, y = as.factor(scenario), fill = model)) +
  ggridges::geom_density_ridges(alpha = 0.5) +
  scale_fill_manual(values = c("navy", "purple"), name = "Model") +
  ylab("# Additional ARMC") +
  xlab("Bites per 100k persons")
